Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars

### 2018-07-15 main.tex
spelling check and font resize in res plots

%\documentclass[twocolumn]{aastex61}
%\pdfoutput=1 %for arXiv submission
\documentclass[fleqn,usenatbib,useAMS]{mnras}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
%\usepackage{pdflscape}	% Landscape pages

@@

\hypersetup{draft}
%\usepackage{multirow}
%\usepackage{mathtools}
%\renewcommand*{\sectionautorefname}{Section} %for \autoref
%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
%\usepackage{graphicx}

%\usepackage{apjfonts} 
%\usepackage{natbib} % bibliography

@@

%\shorttitle{Feedback with Individual Stars}
%\shortauthors{Emerick, Bryan, Mac Low}
\newcommand{\msun}{M$_{\odot}$}
\newcommand{\ccunit}{cm$^{-3}$}

%%%%%%%%%%%%%%%%%%\hypersetup{draft}
% For bibtex

@@

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe. Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$. This is a free parameter in our model; we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017a} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model. We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.

@@

\item 
The gas scale height is thin ($\sim 50$~pc), yet resolved, 
beyond our stellar radius, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius. This is comparable to the resolution limit of the diffuse HI in observed, gaseous ultrafaint dwarfs. At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8--4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Figure~\ref{fig:scale_height}).

@@

Theses differences in densities are shown clearly by comparing Figure~\ref{fig:phase_diagram} with Figure~\ref{fig:phase_resolution}. Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations. In the 7.2~pc run, the gas phases are notably less distinct, with gas more evenly smoothed out in the multi-phase region between cold, dense gas and warm, ionized gas. We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature ceiling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.

>>>>

\documentclass[fleqn,usenatbib,useAMS]{mnras}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
%\usepackage{pdflscape}	% Landscape pages

@@

%\hypersetup{draft}
%\usepackage{multirow}
%\usepackage{mathtools}
%\renewcommand*{\sectionautorefname}{Section} %for \autoref
%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
%\usepackage{graphicx}
%\usepackage{natbib} % bibliography

@@

\newcommand{\msun}{M$_{\odot}$}
\newcommand{\ccunit}{cm$^{-3}$}

@@

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe. Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$; we take $M_{\rm trans} = 8$~M$_{\odot}$. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017a} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model. We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.

@@

\item 
The gas scale height is thin ($\sim 50$~pc), yet resolved, 
beyond our stellar radius, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius. This is comparable to the resolution limit of the diffuse HI in observed, gaseous ultrafaint dwarfs. At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Figure~\ref{fig:scale_height}).

@@

Theses differences in densities are shown clearly by comparing Figure~\ref{fig:phase} with Figure~\ref{fig:phase_resolution}. Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations. In the 7.2~pc run, the gas phases are notably less distinct, with gas more evenly smoothed out in the multi-phase region between cold, dense gas and warm, ionized gas. We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature ceiling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.
